Copies/mL

### 2023-01-31 code/processing_code/copies_calculator.qmd
Total Vibrio Figures

Go from CQ --> Copies/mL
```{r}
data3<- data2 %>%
    mutate(
    log_sq = ((Cq-36.114)/-3.3844), #Equation of the line to get log(SQ)
    sq = 10^log_sq, #Unlog 
    copies_rxn = sq*10, #SQ*Reaction Volume
    copies_uL_1_10 = copies_rxn/2.5, #Copies/RXN / DNA Template Volume
    copies_uL_extract = copies_uL_1_10 *dilution, #(Copies/uL of 1:10)*(1 if there was no sample dilution // *10 if there was a 1:10 dilution etc.)
    concentration_factor = 100/filter_amt, #(Concentration factor = amount of eulted DNA from ZYMO) / (filter amount from vacuum filtration)
    copies_mL = copies_uL_extract*concentration_factor) %>%

@@

Take the average of qPCR triplicates 
```{r}
data5<- data4%>% group_by(Sample,site) %>% #Group all chr together. All that should be left out is the numeric vector we want to work with (in this case, copies_mL)
  summarize_if(is.numeric, mean) %>%
  ungroup() 
```

>>>>

Go from CQ --> Copies/mL
```{r}
data3<- data2 %>%
    mutate(
    log_sq = ((Cq-36.114)/-3.3844), #Equation of the line to get log(SQ)
    sq = 10^log_sq, #Unlog 
    copies_rxn = sq*10, #SQ*Reaction Volume
    copies_uL_1_10 = copies_rxn/2.5, #Copies/RXN / DNA Template Volume
    copies_uL_extract = copies_uL_1_10 *dilution, #(Copies/uL of 1:10)*(1 if there was no sample dilution // *10 if there was a 1:10 dilution etc.)
    concentration_factor = 100/filter_amt, #(Concentration factor = amount of eluted DNA from ZYMO) / (filter amount from vacuum filtration)
    copies_mL = copies_uL_extract*concentration_factor) %>%

@@

Take the average of qPCR triplicates 
```{r}
data5<- data4%>% group_by(Sample,site) %>% #Group all chr together. All that should be left out is the numeric vector we want to work with (in this case, copies_mL)
  summarize_if(is.numeric, mean) %>%
  ungroup() #Ungroup to spit everything back out
```
